Trauma treatment delay

### 2023-11-20 manuscriptlongversion.Rmd
code

As we see in the results, there was only one variable that, when
adjusted, had a correlation with the risk for a patient of receiving
delayed treatment, being the highest hospital care level. Compared with
having the ER as the highest care level, patients who were in the ICU or
the OR had a substantially lowered chance of receiving delayed
treatment.

>>>>

As we see in the results, there was one variable that, when adjusted,
had a correlation with the risk for a patient of receiving delayed
treatment, being the highest hospital care level. Compared with having
the ER as the highest care level, patients who were in the ICU or the OR
had a substantially lowered chance of receiving delayed treatment.

The other variable that when adjusted for had a correlation with
receiving delayed treatment was getting a emergency procedure. Compared
to not receiving an emergency measure, all observed emergency procedures
had a correlation with lower chance of delayed treatment.
